Triptych

### 2019-10-23 paper/main.tex
Aggregation coefficients for soundness proof

The prover then performs these steps:
\begin{itemize}
\item Define $\left\{J^{(u)}\right\}_{u=0}^{w-1} \subset \G$ such that $J^{(u)} \equiv (r^{(u)})^{-1}\hp(M_{l_u})$.
\item Select random $r_A \in \F$ and $\left\{a^{(u)}_{j,i}\right\}_{i=1,j,u=0}^{n-1,m-1,w-1} \subset \F$.
Define $A \equiv \com(a,r_A)$.
\item Define $\left\{\sigma^{(u)}_{j,i}\right\}_{i,j,u=0}^{n-1,j-1,w-1} \subset \F$ such that $\sigma^{(u)}_{j,i} \equiv \delta\left(l^{(u)}_j,i\right)$ (using our decomposition notation), and choose random $r_B \in \F$.
Define $B \equiv \com(\sigma,r_B)$.
\item Select random $r_C \in \F$, and define $C \equiv \com(a(1-2\sigma), r_C)$.
\item Select random $r_D \in \F$, and define $D \equiv \com(-a^2, r_D)$.
\item Select random $\left\{\rho^{(u)}_j\right\}_{j,u=0}^{m-1,w-1}, \left\{\overline{\rho}^{(u)}_j\right\}_{j,u=0}^{m-1,w-1} \subset \F$.
\item For each $0 \leq u < w$, define coefficients $\left\{p^{(u)}_{k,j}\right\}_{k,j=0}^{N-1,m-1}$ such that $$p^{(u)}_k(x) \equiv \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} = \delta\left(l^{(u)},k\right)x^m + \sumj p^{(u)}_{k,j}x^j$$ (using our decomposition notation).
Then define $p_{k,j} \equiv \sumu p^{(u)}_{k,j}$ and $p_k(x) \equiv \sumu p^{(u)}_k(x)$ accordingly.
\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}M_k + \sumu \rho^{(u)}_jG$$
\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv \sumk p_{k,j}\hp(M_k) + \sumu \rho^{(u)}_jJ^{(u)}$$
\item Define $\{Z_j\}_{j=0}^{m-1} \subset \G$ such that: $$Z_j \equiv \sumk p_{k,j}P_k + \sumu \overline{\rho}^{(u)}_jG$$
\item Define the Fiat-Shamir transcript challenge $x \in \F$ computed using all public parameters and these elements (with set notation dropped for brevity): $$M,P,Q,J,A,B,C,D,X,Y,Z$$
\item Define $\left\{f^{(u)}_{j,i}\right\}_{i=1,j,u=0}^{n-1,m-1,w-1}$ such that $f^{(u)}_{j,i} \equiv \sigma^{(u)}_{j,i}x + a^{(u)}_{j,i}$.
\item Define $z_A \equiv r_A + xr_B$ and $z_C \equiv xr_C + r_D$.
\item Define $\left\{z^{(u)}_R\right\}_{u=0}^{w-1} \subset \F$ such that: $$z^{(u)}_R \equiv r^{(u)}x^m - \sumj \rho^{(u)}_jx^j$$
\item Define: $$z_S \equiv x^m\left( \sumu s^{(u)} - \sum_{j=0}^{T-1} t_j \right) - \sumj \left(x^j \sumu \overline{\rho}^{(u)}_j\right)$$
\end{itemize}

@@

All prover-supplied elements are checked to ensure their membership in the proper set (either the scalar field $\F$ or the group $\G$, as appropriate).
The verifier uses the public parameters and proof elements to construct the Fiat-Shamir transcript challenge $x$, and then performs these steps:
\begin{itemize}
\item Ensure that each $J^{(u)}$ is unique for $0 \leq u < w$.
Reject otherwise.
\item For all $0 \leq u < w$ and $0 \leq j < m$, set: $$f^{(u)}_{j,0} \equiv x - \sum_{i=1}^{n-1} f^{(u)}_{j,i}$$
\item{($A/B$ check)} Check that $\com(f,z_A) = A + xB$ and reject otherwise.
\item{($C/D$ check)} Check that $\com(f(x-f),z_C) = xC + D$ and reject otherwise.
\item{($X$ check)} Check that $$\sumk M_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jX_j - \sumu z^{(u)}_RG = 0$$ and reject otherwise.
\item{($Y$ check)} Check that $$\sumk \hp(M_k) \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jY_j - \sumu z^{(u)}_RJ^{(u)} = 0$$ and reject otherwise.
\item{($Z$ check)} Check that $$\sumk P_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jZ_j - x^m\sum_{j=0}^{T-1} Q_j - z_SG = 0$$ and reject otherwise.
\end{itemize}

@@

To show the correctness of the $X$ check:
\begin{eqnarray*}
&& \sumk M_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jX_j - \sumu z^{(u)}_RG \\
&=& \sumk M_k p_k(x) - \sumj x^j \left( \sumk p_{k,j}M_k + \sumu \rho^{(u)}_jG \right) - \sumu z^{(u)}_RG \\
&=& \sumk M_k \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \rho^{(u)}_jG - \sumu z^{(u)}_RG \\
&=& \sumk M_k \left[ \sumu \delta\left( l^{(u)},k \right) \right] - \sumj x^j \sumu \rho^{(u)}_jG - \sumu\left[ r^{(u)}x^m - \sumj \rho^{(u)}_jx^j \right]G \\
&=& x^m\sumu r^{(u)}G - \sumj x^j \sumu \rho^{(u)}_jG - x^m\sumu r^{(u)}G + \sumj x^j \sumu \rho^{(u)}_jG \\
&=& 0
\end{eqnarray*}

The $Y$-check proceeds similarly, but with more irritating algebra:
\begin{eqnarray*}
&& \sumk \hp(M_k) \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jY_j - \sumu z^{(u)}_RJ^{(u)} \\
&=& \sumk \hp(M_k) p_k(x) - \sumj x^j \left( \sumk p_{k,j}\hp(M_k) + \sumu \rho^{(u)}_jJ^{(u)} \right) - \sumu z^{(u)}_RJ^{(u)} \\
&=& \sumk \hp(M_k) \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \rho^{(u)}_jJ^{(u)} - \sumu z^{(u)}_RJ^{(u)} \\
&=& \sumk \hp(M_k) \left[ \sumu \delta\left( l^{(u)},k \right) \right] - \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}\hp(M_{l^{(u)}}) - \sumu\left[ r^{(u)}x^m - \sumj \rho^{(u)}_jx^j \right](r^{(u)})^{-1}\hp(M_{l^{(u)}}) \\
&=& x^m\sumu \hp(M_{l^{(u)}}) - \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}\hp(M_{l^{(u)}}) - x^m\sumu \hp(M_{l^{(u)}}) + \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}\hp(M_{l^{(u)}}) \\
&=& 0
\end{eqnarray*}

>>>>

The prover then performs these steps:
\begin{itemize}
\item Define $\left\{J^{(u)}\right\}_{u=0}^{w-1} \subset \G$ such that $J^{(u)} \equiv (r^{(u)})^{-1}\hp(M_{l_u})$.
\item Select random $r_A \in \F$ and $\left\{a^{(u)}_{j,i}\right\}_{i=1,j,u=0}^{n-1,m-1,w-1} \subset \F$.
Define $A \equiv \com(a,r_A)$.
\item Define $\left\{\sigma^{(u)}_{j,i}\right\}_{i,j,u=0}^{n-1,j-1,w-1} \subset \F$ such that $\sigma^{(u)}_{j,i} \equiv \delta\left(l^{(u)}_j,i\right)$ (using our decomposition notation), and choose random $r_B \in \F$.
Define $B \equiv \com(\sigma,r_B)$.
\item Select random $r_C \in \F$, and define $C \equiv \com(a(1-2\sigma), r_C)$.
\item Select random $r_D \in \F$, and define $D \equiv \com(-a^2, r_D)$.
\item Select random $\left\{\rho^{(u)}_j\right\}_{j,u=0}^{m-1,w-1}, \left\{\overline{\rho}^{(u)}_j\right\}_{j,u=0}^{m-1,w-1} \subset \F$.
\item For each $0 \leq u < w$, define coefficients $\left\{p^{(u)}_{k,j}\right\}_{k,j=0}^{N-1,m-1}$ such that $$p^{(u)}_k(x) \equiv \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} = \delta\left(l^{(u)},k\right)x^m + \sumj p^{(u)}_{k,j}x^j$$ (using our decomposition notation).
Then define $p_{k,j} \equiv \sumu p^{(u)}_{k,j}$ and $p_k(x) \equiv \sumu p^{(u)}_k(x)$ accordingly.
\item Define aggregation coefficients $\{\mu_k\}_{k=0}^{N-1}$ using a $k$-indexed $\hs$ operation, containing all public parameters and proof elements.
\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}\mu_kM_k + \sumu \rho^{(u)}_jG$$
\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv \sumk p_{k,j}\mu_k\hp(M_k) + \sumu \rho^{(u)}_jJ^{(u)}$$
\item Define $\{Z_j\}_{j=0}^{m-1} \subset \G$ such that: $$Z_j \equiv \sumk p_{k,j}P_k + \sumu \overline{\rho}^{(u)}_jG$$
\item Define the Fiat-Shamir transcript challenge $x \in \F$ computed using all public parameters and these elements (with set notation dropped for brevity): $$M,P,Q,J,A,B,C,D,X,Y,Z$$
\item Define $\left\{f^{(u)}_{j,i}\right\}_{i=1,j,u=0}^{n-1,m-1,w-1}$ such that $f^{(u)}_{j,i} \equiv \sigma^{(u)}_{j,i}x + a^{(u)}_{j,i}$.
\item Define $z_A \equiv r_A + xr_B$ and $z_C \equiv xr_C + r_D$.
\item Define $\left\{z^{(u)}_R\right\}_{u=0}^{w-1} \subset \F$ such that: $$z^{(u)}_R \equiv \mu_{l^{(u)}}r^{(u)}x^m - \sumj \rho^{(u)}_jx^j$$
\item Define: $$z_S \equiv x^m\left( \sumu s^{(u)} - \sum_{j=0}^{T-1} t_j \right) - \sumj \left(x^j \sumu \overline{\rho}^{(u)}_j\right)$$
\end{itemize}

@@

All prover-supplied elements are checked to ensure their membership in the proper set (either the scalar field $\F$ or the group $\G$, as appropriate).
The verifier uses the public parameters and proof elements to construct the Fiat-Shamir transcript challenge $x$ and aggregation coefficients $\{\mu_k\}_{k=0}^{N-1}$, and then performs these steps:
\begin{itemize}
\item Ensure that each $J^{(u)}$ is unique for $0 \leq u < w$.
Reject otherwise.
\item For all $0 \leq u < w$ and $0 \leq j < m$, set: $$f^{(u)}_{j,0} \equiv x - \sum_{i=1}^{n-1} f^{(u)}_{j,i}$$
\item{($A/B$ check)} Check that $\com(f,z_A) = A + xB$ and reject otherwise.
\item{($C/D$ check)} Check that $\com(f(x-f),z_C) = xC + D$ and reject otherwise.
\item{($X$ check)} Check that $$\sumk \mu_kM_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jX_j - \sumu z^{(u)}_RG = 0$$ and reject otherwise.
\item{($Y$ check)} Check that $$\sumk \mu_k\hp(M_k) \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jY_j - \sumu z^{(u)}_RJ^{(u)} = 0$$ and reject otherwise.
\item{($Z$ check)} Check that $$\sumk P_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jZ_j - x^m\sum_{j=0}^{T-1} Q_j - z_SG = 0$$ and reject otherwise.
\end{itemize}

@@

To show the correctness of the $X$ check:
\begin{eqnarray*}
&& \sumk \mu_kM_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jX_j - \sumu z^{(u)}_RG \\
&=& \sumk \mu_kM_k p_k(x) - \sumj x^j \left( \sumk p_{k,j}\mu_kM_k + \sumu \rho^{(u)}_jG \right) - \sumu z^{(u)}_RG \\
&=& \sumk \mu_kM_k \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \rho^{(u)}_jG - \sumu z^{(u)}_RG \\
&=& \sumk \mu_kM_k \left[ \sumu \delta\left( l^{(u)},k \right) \right] - \sumj x^j \sumu \rho^{(u)}_jG - \sumu\left[ \mu_{l^{(u)}}r^{(u)}x^m - \sumj \rho^{(u)}_jx^j \right]G \\
&=& x^m\sumu \mu_{l^{(u)}}r^{(u)}G - \sumj x^j \sumu \rho^{(u)}_jG - x^m\sumu \mu_{l^{(u)}}r^{(u)}G + \sumj x^j \sumu \rho^{(u)}_jG \\
&=& 0
\end{eqnarray*}

The $Y$-check proceeds similarly, but with more irritating algebra:
\begin{eqnarray*}
&& \sumk \mu_k\hp(M_k) \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jY_j - \sumu z^{(u)}_RJ^{(u)} \\
&=& \sumk \mu_k\hp(M_k) p_k(x) - \sumj x^j \left( \sumk p_{k,j}\mu_k\hp(M_k) + \sumu \rho^{(u)}_jJ^{(u)} \right) - \sumu z^{(u)}_RJ^{(u)} \\
&=& \sumk \mu_k\hp(M_k) \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \rho^{(u)}_jJ^{(u)} - \sumu z^{(u)}_RJ^{(u)} \\
&=& \sumk \mu_k\hp(M_k) \left[ \sumu \delta\left( l^{(u)},k \right) \right] - \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}\hp(M_{l^{(u)}}) - \sumu\left[ \mu_{l^{(u)}}r^{(u)}x^m - \sumj \rho^{(u)}_jx^j \right](r^{(u)})^{-1}\hp(M_{l^{(u)}}) \\
&=& x^m\sumu \mu_{l^{(u)}}\hp(M_{l^{(u)}}) - \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}\hp(M_{l^{(u)}}) - x^m\sumu \mu_{l^{(u)}}\hp(M_{l^{(u)}}) + \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}\hp(M_{l^{(u)}}) \\
&=& 0
\end{eqnarray*}
